Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-17 3dpas_intro.tex
more work on applications.

In this document, some of our applications are really {\em traditional
  applications}, meaning a program that is developed by a user or project to try
to answer a science question, usually with some input data needed and some
output data produced.  Applications in this category are: NGS (next generation
sequencing) Analytics (\S\ref{bioSilvia}), CMB (cosmic microwave background)
(\S\ref{astroJulian}), Fusion (\S\ref{fusionScott}), Industrial Incident
Notification and Response (\S\ref{Kees}), MODIS (moderate resolution imaging
spectroradiometer) Data Processing (\S\ref{modisKeith}), and Distributed Network
Intrusion Detection (\S\ref{detectionJon}).

@@

In other words, multiple infrastructural applications are used together in particular
science domains.  Furthermore, infrastructural
applications involve more than just the end user (scientist), and
typically require exerting control at layers below, i.e.,
``programming the system (infrastructure)'', as opposed to a
traditional applications, where end user effort and control is often
confined to a well-defined application kernel.

>>>>

% In this document, some of our applications are really {\em traditional
% applications}, meaning a program that is developed by a user or project to try
% to answer a science question, usually with some input data needed and some
% output data produced.

Against this backdrop, we eschew a formal classification of application types,
however, to facilitate understanding we categorise applications into two
categories: the first is that of {\em traditional applications}, where
% traditional is  applications are {\em traditional applications}, in that 
a program (or set of programs) is developed by a user or project to try to
answer a science question (or set of related questions). Traditional application
might A single standalone computer program, a distributed application or a
complex workflow could fall under the category of a {\em traditional
  application}.  Applications in this category are: NGS (next generation
sequencing) Analytics (\S\ref{bioSilvia}), CMB (cosmic microwave background)
(\S\ref{astroJulian}), Fusion (\S\ref{fusionScott}), Industrial Incident
Notification and Response (\S\ref{Kees}), MODIS (moderate resolution imaging
spectroradiometer) Data Processing (\S\ref{modisKeith}), and Distributed Network
Intrusion Detection (\S\ref{detectionJon}).

@@

In other words, multiple infrastructural applications are used together in
particular science domains.  Furthermore, infrastructural applications involve
more than just the end user (scientist), and typically require exerting control
at layers below, i.e., ``programming the system (infrastructure)'', as opposed
to a traditional applications, where end user effort and control is often
confined to a well-defined application kernel and their communication and
coordination.  Also, for some {\em traditional applications} (e.g., NGS) the
number of users of an instance of the application is typically small, i.e., the
predominant use is by the long-tail of science. In contrast, some
infrastructural applications are correlated with ``big science'' projects.
